Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-03-15 ConferencePaper/DraftEdwardsWoods.Rnw
Paper now has a few descriptive statistics tables and the orthodox model outputs.  The model outputs are not in an easy to read form and needs work.

@@

<<echo=FALSE,results=hide>>=
#work only with this subset
RECS<-RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]
@

@@

  \subsection{Race and Ethnicity Differences in Equipment and Structure}
  \subsection{Differences in Reported Behavior}

@@

  \subsection{Orthodox Results}
  \subsection{Single Equation Methods}
  \subsection{Multiple Equation Methods}

>>>>

HUD <- read.csv("HUD.csv")

#And the clean up from importing from excell
HUD$pop<-as.numeric(gsub(",","",HUD$pop))
HUD$reportablen<-as.factor(HUD$reportablen)
summary(HUD)
CritHUD<-unique(HUD[c("reportablen","reporttot")])
RECS<-merge(RECS,CritHUD, by.x="REPORTABLE_DOMAIN", by.y="reportablen")

}

@@

<<DataSubset,echo=FALSE,results=hide>>=
#work only with this subset
RECS<-RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]
if(!file.exists("RECS.RData"))save(RECS,file="RECS.RData")

@@

<<tabRaceVStruct,echo=false,results=tex>>=
library(xtable)
xtable(table(RECS$TYPEHUQ,RECS$EthRace), caption="Count of Observations by Race and Structure Type", label="tab:RaceVStruct")
@

\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
<<echo=false,fig=TRUE>>=
library(ggplot2)
qplot(KWH, data = RECS, xlim=c(0,30000),facets =EthRace~KOWNRENT, geom = "density" )
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Annual kWh by Income}
\label{fig:kWhbyIncome}
<<echo=false,fig=TRUE>>=
library(ggplot2)
qplot(Income,KWH, data = RECS, xlim=c(0,30000),facets =EthRace~KOWNRENT )+geom_boxplot()
@
\end{center}
\end{figure}

  \subsection{Race and Ethnicity Differences in Equipment and Structure}

  \subsection{Differences in Reported Behavior}

  \subsection{HUD Complaints}

<<echo=false,results=tex>>=
library(xtable)
HUD<-read.csv("HUD.csv")
HUDCut<-HUD[c("state","pop","reporttot")]
names(HUDCut)<-c("State","Population","Reports (per 100,000)")

#***TODO Fix so it does not show the row number***
xtable(HUDCut,caption="HUD Complaints per 100,000 Population", label="tab:HUDComplaints")
rm(HUD)
@

@@

  \subsection{Orthodox Results}

<<OrthodoxKWH, echo=FALSE, results=tex>>=

OrthodoxKWH<-lm(KWH~StrTenure:TOTSQFT_EN:HDD65+StrTenure:TOTSQFT_EN:CDD65 
           + ElecMeals
           + NUMFRIG+AgeFridge
           + TVONWD1:TVTYPE1
           + NUMPC+TIMEON1
           + WELLPUMP
           + ElecWater
           + SWIMPOOL + ElecPool
           + RECBATH +ElecTub
           + TYPEGLASS:TOTSQFT_EN
           + NHSLDMEM
           + Income+EthRace:Income, data=RECS,weights=NWEIGHT)
xtable(OrthodoxKWH,caption="Orthodox kWh Model",label="tab:OrthoKWH")
@

<<OrthodoxSQFT, echo=FALSE,results=tex>>=
# Replicating what Edwards did in Stata.
# reg totsqft_encat rentass ownrent dweltype lnincome nhsldmem reporttot reporttot i.education 
# i.householder_race#c.reporttot urbanrural

OrthodoxSQFT<-lm(TOTSQFT_EN~RENTHELP+StrTenure+Income+reporttot+reporttot:EthRace+EDUCATION+UR, data=RECS)
xtable(OrthodoxSQFT,caption="Orthodox Square Foot Model",label="tab:OrthoSQFT")

<<OrthodoxStructTenure,echo=FALSE,results=tex>>=

  \subsection{Single Equation Methods}
  \subsection{Multiple Equation Methods}

### 2015-03-15 ConferencePaper/DraftEdwardsWoods.tex
Paper now has a few descriptive statistics tables and the orthodox model outputs.  The model outputs are not in an easy to read form and needs work.

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sat Mar 14 21:27:10 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Wt & AfAm & NativeAm & Asian & Pacific & Other & Multi \\ 
  \hline
Mobile & 468 &  27 &   9 &   1 &   1 &   8 &   7 \\ 
  SFDetached & 6424 & 762 &  52 & 236 &  24 & 100 &  97 \\ 
  SFAttached & 649 & 131 &  12 &  48 &   2 &  20 &  16 \\ 
  SmApartment & 614 & 179 &  13 &  52 &   3 &  29 &  16 \\ 
  LgApartment & 1283 & 390 &  24 & 114 &  10 &  53 &  31 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-004}
\end{center}
\end{figure}

@@

\section{Conditional Demand Estimation}

  \subsection{Orthodox Results}
  \subsection{Single Equation Methods}
  \subsection{Multiple Equation Methods}

>>>>

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:51:59 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrrrrrrr}
  \hline
 & FALSEWt & FALSEAfAm & FALSEAsian & FALSEMulti & FALSENativeAm & FALSEOther & FALSEPacific & TRUEAfAm & TRUEAsian & TRUEMulti & TRUENativeAm & TRUEOther & TRUEPacific & TRUEWt \\ 
  \hline
Mobile & 371 &  24 &   1 &   6 &   7 &   2 &   1 &   3 &   0 &   1 &   2 &   6 &   0 &  97 \\ 
  SFDetached & 5694 & 754 & 231 &  87 &  35 &  59 &  22 &   8 &   5 &  10 &  17 &  41 &   2 & 730 \\ 
  SFAttached & 544 & 121 &  48 &  14 &   9 &   8 &   1 &  10 &   0 &   2 &   3 &  12 &   1 & 105 \\ 
  SmApartment & 430 & 174 &  52 &  12 &   7 &  13 &   2 &   5 &   0 &   4 &   6 &  16 &   1 & 184 \\ 
  LgApartment & 951 & 382 & 113 &  27 &  15 &  29 &  10 &   8 &   1 &   4 &   9 &  24 &   0 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-004}
\end{center}
\end{figure}

@@

  \subsection{HUD Complaints}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:52:15 2015
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & State & Population & Reports (per 100,000) \\ 
  \hline
1 & Alabama & 4,677,464 & 7.50 \\ 
  2 & Alaska & 688,125 & 13.01 \\ 
  3 & Arizona & 6,499,377 & 3.68 \\ 
  4 & Arkansas & 2,867,764 & 9.26 \\ 
  5 & California & 36,580,371 & 3.03 \\ 
  6 & Colorado & 4,935,213 & 1.97 \\ 
  7 & Connecticut & 3,502,932 & 20.50 \\ 
  8 & Delaware & 876,211 & 14.00 \\ 
  9 & District of Columbia & 590,074 & 14.00 \\ 
  10 & Florida & 18,423,878 & 3.93 \\ 
  11 & Georgia & 9,697,838 & 2.06 \\ 
  12 & Hawaii & 1,287,481 & 13.01 \\ 
  13 & Idaho & 1,527,506 & 9.94 \\ 
  14 & Illinois & 12,842,954 & 2.88 \\ 
  15 & Indiana & 6,388,309 & 9.14 \\ 
  16 & Iowa & 2,993,987 & 19.92 \\ 
  17 & Kansas & 2,797,375 & 10.31 \\ 
  18 & Kentucky & 4,287,931 & 7.50 \\ 
  19 & Louisiana & 4,451,513 & 9.26 \\ 
  20 & Maine & 1,319,691 & 20.50 \\ 
  21 & Maryland & 5,658,655 & 14.00 \\ 
  22 & Massachusetts & 6,543,595 & 4.51 \\ 
  23 & Michigan & 10,002,486 & 4.97 \\ 
  24 & Minnesota & 5,230,567 & 19.92 \\ 
  25 & Mississippi & 2,940,212 & 7.50 \\ 
  26 & Missouri & 5,956,335 & 4.99 \\ 
  27 & Montana & 968,035 & 9.94 \\ 
  28 & Nebraska & 1,781,949 & 10.31 \\ 
  29 & Nevada & 2,615,772 & 5.08 \\ 
  30 & New Hampshire & 1,321,872 & 20.50 \\ 
  31 & New Jersey & 8,663,398 & 2.34 \\ 
  32 & New Mexico & 1,986,763 & 5.08 \\ 
  33 & New York & 19,467,789 & 4.60 \\ 
  34 & North Carolina & 9,247,134 & 4.22 \\ 
  35 & North Dakota & 641,421 & 19.92 \\ 
  36 & Ohio & 11,528,072 & 9.14 \\ 
  37 & Oklahoma & 3,644,025 & 9.26 \\ 
  38 & Oregon & 3,782,991 & 13.01 \\ 
  39 & Pennsylvania & 12,566,368 & 1.87 \\ 
  40 & Rhode Island & 1,053,502 & 20.50 \\ 
  41 & South Carolina & 4,503,280 & 4.22 \\ 
  42 & South Dakota & 804,532 & 19.92 \\ 
  43 & Tennessee & 6,240,456 & 2.61 \\ 
  44 & Texas & 24,304,290 & 4.18 \\ 
  45 & Utah & 2,727,343 & 9.94 \\ 
  46 & Vermont & 621,049 & 20.50 \\ 
  47 & Virginia & 7,795,424 & 2.03 \\ 
  48 & Washington & 6,566,073 & 13.01 \\ 
  49 & West Virginia & 1,814,873 & 14.00 \\ 
  50 & Wisconsin & 5,627,610 & 1.81 \\ 
  51 & Wyoming & 532,981 & 9.94 \\ 
   \hline
\end{tabular}
\caption{HUD Complaints per 100,000 Population} 
\label{tab:HUDComplaints}
\end{table}
\section{Conditional Demand Estimation}

  \subsection{Orthodox Results}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:52:15 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 2181.1197 & 1792.3947 & 1.22 & 0.2237 \\ 
  ElecMealsThreeDay & 1338.6588 & 297.7217 & 4.50 & 0.0000 \\ 
  ElecMealsTwoDay & 1644.3185 & 185.0764 & 8.88 & 0.0000 \\ 
  ElecMealsOneDay & 1685.3404 & 159.1570 & 10.59 & 0.0000 \\ 
  ElecMealsFewWeek & 1451.1356 & 183.7584 & 7.90 & 0.0000 \\ 
  ElecMealsOneWeek & 1726.8842 & 406.3322 & 4.25 & 0.0000 \\ 
  ElecMealsLessWeek & 992.8116 & 424.8594 & 2.34 & 0.0195 \\ 
  NUMFRIG & 1574.9574 & 120.8432 & 13.03 & 0.0000 \\ 
  AgeFridge2to4Years & 49.6457 & 195.1174 & 0.25 & 0.7992 \\ 
  AgeFridge5to9Years & 312.9075 & 183.1243 & 1.71 & 0.0875 \\ 
  AgeFridge20PlusYears & 282.4503 & 328.6753 & 0.86 & 0.3902 \\ 
  AgeFridge10to14Years & 392.2705 & 207.4396 & 1.89 & 0.0587 \\ 
  AgeFridge15to19Years & 3.4299 & 283.6629 & 0.01 & 0.9904 \\ 
  NUMPC & 345.0370 & 64.3126 & 5.37 & 0.0000 \\ 
  TIMEON1OneTo3Hrs & -142.2026 & 160.6198 & -0.89 & 0.3760 \\ 
  TIMEON1ThreeTo6Hrs & -5.9463 & 186.4186 & -0.03 & 0.9746 \\ 
  TIMEON1SixTo10Hrs & 224.2810 & 239.0840 & 0.94 & 0.3482 \\ 
  TIMEON1Gr10 & 823.2281 & 214.7291 & 3.83 & 0.0001 \\ 
  WELLPUMPTRUE & 1501.4018 & 183.5027 & 8.18 & 0.0000 \\ 
  ElecWaterSmall & 4421.9192 & 256.3522 & 17.25 & 0.0000 \\ 
  ElecWaterMed & 4658.3555 & 163.9114 & 28.42 & 0.0000 \\ 
  ElecWaterLrg & 5809.5827 & 189.7584 & 30.62 & 0.0000 \\ 
  ElecWaterTankless & 3251.7517 & 755.3718 & 4.30 & 0.0000 \\ 
  SWIMPOOLTRUE & 3228.7285 & 222.3292 & 14.52 & 0.0000 \\ 
  ElecPoolTRUE & 4604.1557 & 837.0574 & 5.50 & 0.0000 \\ 
  RECBATHTRUE & 1013.4653 & 426.3413 & 2.38 & 0.0175 \\ 
  ElecTubTRUE & 1218.8041 & 486.6005 & 2.50 & 0.0123 \\ 
  NHSLDMEM & 952.0720 & 42.5506 & 22.38 & 0.0000 \\ 
  Income & 0.0086 & 0.0016 & 5.37 & 0.0000 \\ 
  TVONWD1LessHour:TVTYPE1Standard & -3266.1101 & 1800.2730 & -1.81 & 0.0697 \\ 
  TVONWD1OneTo3Hrs:TVTYPE1Standard & -3010.1255 & 1775.5111 & -1.70 & 0.0900 \\ 
  TVONWD1ThreeTo6Hrs:TVTYPE1Standard & -2516.9211 & 1772.6818 & -1.42 & 0.1557 \\ 
  TVONWD1SixTo10Hrs:TVTYPE1Standard & -1794.7156 & 1778.9345 & -1.01 & 0.3131 \\ 
  TVONWD1Gr10:TVTYPE1Standard & -1290.6207 & 1784.9518 & -0.72 & 0.4697 \\ 
  TVONWD1LessHour:TVTYPE1LCD & -2896.8097 & 1807.2466 & -1.60 & 0.1090 \\ 
  TVONWD1OneTo3Hrs:TVTYPE1LCD & -2313.1891 & 1773.9814 & -1.30 & 0.1923 \\ 
  TVONWD1ThreeTo6Hrs:TVTYPE1LCD & -1955.8036 & 1770.9445 & -1.10 & 0.2695 \\ 
  TVONWD1SixTo10Hrs:TVTYPE1LCD & -1593.9919 & 1777.1898 & -0.90 & 0.3698 \\ 
  TVONWD1Gr10:TVTYPE1LCD & -485.7205 & 1785.6404 & -0.27 & 0.7856 \\ 
  TVONWD1LessHour:TVTYPE1Plasma & -1497.7500 & 1988.0024 & -0.75 & 0.4512 \\ 
  TVONWD1OneTo3Hrs:TVTYPE1Plasma & -1664.7504 & 1800.8346 & -0.92 & 0.3553 \\ 
  TVONWD1ThreeTo6Hrs:TVTYPE1Plasma & -2001.8306 & 1788.6852 & -1.12 & 0.2631 \\ 
  TVONWD1SixTo10Hrs:TVTYPE1Plasma & -940.8541 & 1815.7684 & -0.52 & 0.6044 \\ 
  TVONWD1Gr10:TVTYPE1Plasma & 418.9083 & 1846.1024 & 0.23 & 0.8205 \\ 
  TVONWD1LessHour:TVTYPE1Projection & -2094.9059 & 2146.9297 & -0.98 & 0.3292 \\ 
  TVONWD1OneTo3Hrs:TVTYPE1Projection & -1639.6049 & 1851.1064 & -0.89 & 0.3758 \\ 
  TVONWD1ThreeTo6Hrs:TVTYPE1Projection & -2152.3377 & 1812.9470 & -1.19 & 0.2352 \\ 
  TVONWD1SixTo10Hrs:TVTYPE1Projection & -925.1902 & 1837.7040 & -0.50 & 0.6147 \\ 
  TVONWD1Gr10:TVTYPE1Projection & 1530.2305 & 1911.2140 & 0.80 & 0.4234 \\ 
  TVONWD1LessHour:TVTYPE1LED & -4513.1128 & 2901.1001 & -1.56 & 0.1198 \\ 
  TVONWD1OneTo3Hrs:TVTYPE1LED & -1678.7884 & 2013.2805 & -0.83 & 0.4044 \\ 
  TVONWD1ThreeTo6Hrs:TVTYPE1LED & -2106.7446 & 1923.5912 & -1.10 & 0.2735 \\ 
  TVONWD1SixTo10Hrs:TVTYPE1LED & -3418.0720 & 2390.7609 & -1.43 & 0.1528 \\ 
  TOTSQFT\_EN:TYPEGLASSSinglePane & -0.1921 & 0.1586 & -1.21 & 0.2259 \\ 
  TOTSQFT\_EN:TYPEGLASSDoublePane & -0.0336 & 0.1540 & -0.22 & 0.8271 \\ 
  TOTSQFT\_EN:TYPEGLASSTriplePane & 0.0093 & 0.2093 & 0.04 & 0.9644 \\ 
  Income:EthRaceFALSEAfAm & 0.0031 & 0.0027 & 1.14 & 0.2548 \\ 
  Income:EthRaceFALSEAsian & -0.0243 & 0.0034 & -7.16 & 0.0000 \\ 
  Income:EthRaceFALSEMulti & -0.0168 & 0.0069 & -2.43 & 0.0153 \\ 
  Income:EthRaceFALSENativeAm & 0.0117 & 0.0123 & 0.95 & 0.3425 \\ 
  Income:EthRaceFALSEOther & -0.0249 & 0.0083 & -2.99 & 0.0028 \\ 
  Income:EthRaceFALSEPacific & -0.0163 & 0.0138 & -1.18 & 0.2378 \\ 
  Income:EthRaceTRUEAfAm & -0.0120 & 0.0165 & -0.73 & 0.4672 \\ 
  Income:EthRaceTRUEAsian & -0.0365 & 0.0454 & -0.80 & 0.4219 \\ 
  Income:EthRaceTRUEMulti & -0.0291 & 0.0212 & -1.37 & 0.1693 \\ 
  Income:EthRaceTRUENativeAm & -0.0187 & 0.0148 & -1.26 & 0.2077 \\ 
  Income:EthRaceTRUEOther & -0.0262 & 0.0099 & -2.63 & 0.0085 \\ 
  Income:EthRaceTRUEPacific & -0.0122 & 0.0380 & -0.32 & 0.7474 \\ 
  Income:EthRaceTRUEWt & -0.0192 & 0.0031 & -6.29 & 0.0000 \\ 
  StrTenureOwnSFDetached:TOTSQFT\_EN:HDD65 & 0.0001 & 0.0000 & 4.10 & 0.0000 \\ 
  StrTenureOwnLgApartment:TOTSQFT\_EN:HDD65 & -0.0001 & 0.0001 & -0.96 & 0.3381 \\ 
  StrTenureOwnMobile:TOTSQFT\_EN:HDD65 & 0.0004 & 0.0001 & 5.98 & 0.0000 \\ 
  StrTenureOwnSFAttached:TOTSQFT\_EN:HDD65 & -0.0000 & 0.0000 & -0.55 & 0.5812 \\ 
  StrTenureOwnSmApartment:TOTSQFT\_EN:HDD65 & 0.0000 & 0.0001 & 0.54 & 0.5866 \\ 
  StrTenureRentLgApartment:TOTSQFT\_EN:HDD65 & -0.0002 & 0.0001 & -4.00 & 0.0001 \\ 
  StrTenureRentMobile:TOTSQFT\_EN:HDD65 & 0.0004 & 0.0002 & 1.76 & 0.0779 \\ 
  StrTenureRentSFAttached:TOTSQFT\_EN:HDD65 & 0.0000 & 0.0001 & 0.60 & 0.5479 \\ 
  StrTenureRentSFDetached:TOTSQFT\_EN:HDD65 & 0.0000 & 0.0000 & 0.55 & 0.5813 \\ 
  StrTenureRentSmApartment:TOTSQFT\_EN:HDD65 & -0.0001 & 0.0001 & -1.86 & 0.0632 \\ 
  StrTenureOwnSFDetached:TOTSQFT\_EN:CDD65 & 0.0008 & 0.0000 & 19.21 & 0.0000 \\ 
  StrTenureOwnLgApartment:TOTSQFT\_EN:CDD65 & -0.0002 & 0.0002 & -0.82 & 0.4140 \\ 
  StrTenureOwnMobile:TOTSQFT\_EN:CDD65 & 0.0009 & 0.0001 & 7.32 & 0.0000 \\ 
  StrTenureOwnSFAttached:TOTSQFT\_EN:CDD65 & 0.0006 & 0.0001 & 5.01 & 0.0000 \\ 
  StrTenureOwnSmApartment:TOTSQFT\_EN:CDD65 & 0.0001 & 0.0003 & 0.40 & 0.6875 \\ 
  StrTenureRentLgApartment:TOTSQFT\_EN:CDD65 & 0.0000 & 0.0001 & 0.39 & 0.6946 \\ 
  StrTenureRentMobile:TOTSQFT\_EN:CDD65 & 0.0024 & 0.0004 & 6.32 & 0.0000 \\ 
  StrTenureRentSFAttached:TOTSQFT\_EN:CDD65 & 0.0007 & 0.0002 & 4.02 & 0.0001 \\ 
  StrTenureRentSFDetached:TOTSQFT\_EN:CDD65 & 0.0008 & 0.0001 & 9.27 & 0.0000 \\ 
  StrTenureRentSmApartment:TOTSQFT\_EN:CDD65 & 0.0005 & 0.0002 & 2.84 & 0.0046 \\ 
   \hline
\end{tabular}
\caption{Orthodox kWh Model} 
\label{tab:OrthoKWH}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sun Mar 15 22:52:15 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 1948.2943 & 80.2307 & 24.28 & 0.0000 \\ 
  RENTHELPTRUE & 206.7350 & 84.1076 & 2.46 & 0.0140 \\ 
  StrTenureOwnLgApartment & -1392.2772 & 72.2081 & -19.28 & 0.0000 \\ 
  StrTenureOwnMobile & -1134.4416 & 53.9823 & -21.02 & 0.0000 \\ 
  StrTenureOwnSFAttached & -549.6952 & 49.0434 & -11.21 & 0.0000 \\ 
  StrTenureOwnSmApartment & -779.1076 & 89.4444 & -8.71 & 0.0000 \\ 
  StrTenureRentLgApartment & -1393.4070 & 31.1855 & -44.68 & 0.0000 \\ 
  StrTenureRentMobile & -1213.4556 & 108.7993 & -11.15 & 0.0000 \\ 
  StrTenureRentSFAttached & -856.9121 & 57.0870 & -15.01 & 0.0000 \\ 
  StrTenureRentSFDetached & -553.5699 & 38.5786 & -14.35 & 0.0000 \\ 
  StrTenureRentSmApartment & -1161.1082 & 42.1556 & -27.54 & 0.0000 \\ 
  Income & 0.0078 & 0.0003 & 29.57 & 0.0000 \\ 
  reporttot & 14.8827 & 1.8850 & 7.90 & 0.0000 \\ 
  EDUCATIONNoHS & 98.3357 & 82.3383 & 1.19 & 0.2324 \\ 
  EDUCATIONHS & 109.9418 & 77.9684 & 1.41 & 0.1585 \\ 
  EDUCATIONSomeCol & 168.9859 & 78.5995 & 2.15 & 0.0316 \\ 
  EDUCATIONAA & 171.7528 & 82.0919 & 2.09 & 0.0364 \\ 
  EDUCATIONBA & 352.1423 & 79.7827 & 4.41 & 0.0000 \\ 
  EDUCATIONMA & 369.0524 & 84.7068 & 4.36 & 0.0000 \\ 
  EDUCATIONProf & 623.5784 & 105.4315 & 5.91 & 0.0000 \\ 
  EDUCATIONPHD & 499.0001 & 115.4102 & 4.32 & 0.0000 \\ 
  URUrban & -279.5002 & 25.5669 & -10.93 & 0.0000 \\ 
  reporttot:EthRaceFALSEAfAm & -4.9338 & 4.5597 & -1.08 & 0.2793 \\ 
  reporttot:EthRaceFALSEAsian & -8.7364 & 7.7372 & -1.13 & 0.2589 \\ 
  reporttot:EthRaceFALSEMulti & -18.8675 & 9.8690 & -1.91 & 0.0559 \\ 
  reporttot:EthRaceFALSENativeAm & -14.2408 & 12.0000 & -1.19 & 0.2354 \\ 
  reporttot:EthRaceFALSEOther & 0.6991 & 12.7324 & 0.05 & 0.9562 \\ 
  reporttot:EthRaceFALSEPacific & -37.5385 & 18.1475 & -2.07 & 0.0386 \\ 
  reporttot:EthRaceTRUEAfAm & -13.9581 & 28.5075 & -0.49 & 0.6244 \\ 
  reporttot:EthRaceTRUEAsian & -16.9656 & 33.5615 & -0.51 & 0.6132 \\ 
  reporttot:EthRaceTRUEMulti & 2.8707 & 16.5903 & 0.17 & 0.8626 \\ 
  reporttot:EthRaceTRUENativeAm & -22.4893 & 35.3740 & -0.64 & 0.5249 \\ 
  reporttot:EthRaceTRUEOther & 5.1444 & 11.5405 & 0.45 & 0.6558 \\ 
  reporttot:EthRaceTRUEPacific & -34.7671 & 55.4693 & -0.63 & 0.5308 \\ 
  reporttot:EthRaceTRUEWt & -23.1538 & 5.5814 & -4.15 & 0.0000 \\ 
   \hline
\end{tabular}
\caption{Orthodox Square Foot Model} 
\label{tab:OrthoSQFT}
\end{table}

  \subsection{Single Equation Methods}
  \subsection{Multiple Equation Methods}
